Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-04-02 paper/manuscript.Rmd
adjust to use text ref, fig2
stretch width fig 1 in doc

```{r, fig.cap = '(ref:fig1)'}
knitr::include_graphics('../graphics/IMG_1562.JPG')
```

@@

\captionsetup[figure]{labelformat=empty}

![**Figure 2**: A) Map of the Fogo Island archipelago with swimming events between islands. B) Histogram displaying the distribution of swimming events throughout the year. Note, colours correspond to individual caribou. C) Inset of swimming events between small islands on the northern coast of Fogo island. D) Inset of swimming events between islands on the southern coast of Fogo island. ](../graphics/Fig2.png)

>>>>

```{r, fig.cap = '(ref:fig1)', fig.width=4.5}
knitr::include_graphics('../graphics/IMG_1562_crop.JPG')
```

@@

(ref:fig2) A) Map of the Fogo Island archipelago with swimming events between islands. B) Histogram displaying the distribution of swimming events throughout the year. Note, colours correspond to individual caribou. C) Inset of swimming events between small islands on the northern coast of Fogo island. D) Inset of swimming events between islands on the southern coast of Fogo island.

```{r, fig.cap = '(ref:fig2)'}
knitr::include_graphics('../graphics/Fig2.png')
```
